Prevalence, ANC, ART model inference case-study

### 2022-10-17 src/explore_aghq/aghq.Rmd
marginal_laplace_tmb walkthrough
Add tabs to prev-anc-art plots, small text improvements

---
title: "Understanding the `aghq` package"
author:
- name: Adam Howes
output:
  html_document:
    toc: yes
    toc_float: yes
    toc_collapsed: yes
    df_print: paged
    code_folding: show
    theme: lumen
abstract: |
  **Background**

  **Task**
---

>>>>

---
title: "Understanding the `aghq` package"
author:
- name: Adam Howes
output:
  html_document:
    toc: yes
    toc_float: yes
    toc_collapsed: yes
    df_print: paged
    code_folding: show
    theme: lumen
abstract: |
  **Background** `aghq` is an R package which implements adaptive Gauss-Hermite quadrature.

  **Task** In this notebook, we work through the vignettes for the `aghq` package, adding material as is useful to develop understanding.
---

### 2022-10-17 src/prev-anc-art_process-results/prev-anc-art.Rmd
Add tabs to prev-anc-art plots, small text improvements

    **Task** We compare inferences produced using tmbstan, `TMB` and `aghq` for a collection of HIV evidence synthesis models based upon the Naomi small-area estimation model.

@@

## Model description

@@

### Prevalence component

@@

### ANC component

@@

### ART component

@@

## Implementation

We consider five models as described below.
For each model we write a `TMB` C++ template.
As well as the standard `TMB` inference approach, this template allows the model to be fit using Stan via `tmbstan` and using adaptive Gaussian Hermite quadrature via `aghq`.

@@

## Results

@@

### Boxplots

@@

```{r cache=FALSE}
params <- c("beta_prev", "log_sigma_phi_prev")

draw_boxplots(model1, params = params) + labs(title = "Model 1")
draw_boxplots(model2, params = params) + labs(title = "Model 2")
draw_boxplots(model3, params = params) + labs(title = "Model 3")
draw_boxplots(model4, params = params) + labs(title = "Model 4")
```

### Scatterplots

```{r}
params <- c("beta_prev", "log_sigma_phi_prev")

draw_scatterplots(model1, params = params) + labs(title = "Model 1")
draw_scatterplots(model2, params = params) + labs(title = "Model 2")
draw_scatterplots(model3, params = params) + labs(title = "Model 3")
draw_scatterplots(model4, params = params) + labs(title = "Model 4")
```

### Kolmogorov KS test plots

Take samples from all distributions, then compute maximum ECDF difference $D$ (two-sample Kolmogorov–Smirnov test).
We assume that `tmbstan` represents the gold-standard, and compare performance of `aghq` and `TMB` via their similarity to this gold-standard.
Higher values of $D$ correspond to distributions which are more different.

```{r fig.height=8}
draw_ksplots_D(model1) + labs(title = "Model 1")
draw_ksplots_D(model2) + labs(title = "Model 2")
draw_ksplots_D(model3) + labs(title = "Model 3")
draw_ksplots_D(model4) + labs(title = "Model 4")
```

@@

### MCMC diagnostics

@@

#### Traceplots

@@

```{r}
map(model1, "mcmc_traceplots")
map(model2, "mcmc_traceplots")
map(model3, "mcmc_traceplots")
map(model4, "mcmc_traceplots")
```

#### R hat

@@

```{r}
draw_rhatplot(model1) + labs(title = "Model 1")
draw_rhatplot(model2) + labs(title = "Model 2")
draw_rhatplot(model3) + labs(title = "Model 3")
draw_rhatplot(model4) + labs(title = "Model 4")
```

## Conclusion

## Bibliography {-}

>>>>

    **Task** We compare inferences produced using `tmbstan`, `TMB` and `aghq` for a collection of HIV evidence synthesis models based upon the Naomi small-area estimation model.

@@

# Model description

@@

## Prevalence component

@@

## ANC component

@@

## ART component

@@

# Implementation

We consider five models as described below.
For each model we write a `TMB` C++ template.
As well as the standard `TMB` inference approach, this template allows the model to be fit using Stan via `tmbstan` and using adaptive Gauss-Hermite quadrature via `aghq`.

@@

# Results

@@

## Boxplots {.tabset .tabset-fade}

@@

```{r}
params <- c("beta_prev", "log_sigma_phi_prev")
```

### Model 1

```{r cache=FALSE}
draw_boxplots(model1, params = params) + labs(title = "Model 1")
```

### Model 2

```{r cache=FALSE}
draw_boxplots(model2, params = params) + labs(title = "Model 2")
```

### Model 3

```{r cache=FALSE}
draw_boxplots(model3, params = params) + labs(title = "Model 3")
```

### Model 4

```{r cache=FALSE}
draw_boxplots(model4, params = params) + labs(title = "Model 4")
```

##

## Scatterplots {.tabset .tabset-fade}

Scatterplots of posterior summaries (such as mean and standard deviation) where the $x$-axis is the posterior summary as estimated by `tmbstan` and the $y$-axis is the posterior summary as estimated by either `ahgq` or `TMB`.
We treat `tmbstan` as the gold-standard, so any deviation from the line $y = x$ suggests inaccurate posterior summaries.

```{r}
params <- c("beta_prev", "log_sigma_phi_prev")
```

### Model 1

```{r}
draw_scatterplots(model1, params = params) + labs(title = "Model 1")
```

### Model 2

```{r}
draw_scatterplots(model2, params = params) + labs(title = "Model 2")
```

### Model 3

```{r}
draw_scatterplots(model3, params = params) + labs(title = "Model 3")
```

### Model 4

```{r}
draw_scatterplots(model4, params = params) + labs(title = "Model 4")
```

##

## Kolmogorov KS test plots {.tabset .tabset-fade}

Take samples from all distributions, then compute maximum ECDF difference $D$ (two-sample Kolmogorov–Smirnov test).
On the $y$-axis we plot $\text{KS}(\texttt{TMB}, \texttt{tmbstan})$ and on the $x$-axis $\text{KS}(\texttt{aghq}, \texttt{tmbstan})$.
Lower values of $D$ (minimum possible zero) correspond to more similar distributions, and higher values of $D$ correspond to distributions which are more different.

### Model 1

```{r fig.height=8}
draw_ksplots_D(model1) + labs(title = "Model 1")
```

### Model 2

```{r fig.height=8}
draw_ksplots_D(model2) + labs(title = "Model 2")
```

### Model 3

```{r fig.height=8}
draw_ksplots_D(model3) + labs(title = "Model 3")
```

### Model 4

```{r fig.height=8}
draw_ksplots_D(model4) + labs(title = "Model 4")
```

##

@@

## MCMC diagnostics

@@

### Traceplots {.tabset .tabset-fade}

@@

#### Model 1

```{r}
map(model1, "mcmc_traceplots")
```

#### Model 2

```{r}
map(model2, "mcmc_traceplots")
```

#### Model 3

```{r}
map(model3, "mcmc_traceplots")
```

#### Model 4

```{r}
map(model4, "mcmc_traceplots")
```

###

### R hat {.tabset .tabset-fade}

@@

#### Model 1

```{r}
draw_rhatplot(model1) + labs(title = "Model 1")
```

#### Model 2

```{r}
draw_rhatplot(model2) + labs(title = "Model 2")
```

#### Model 3

```{r}
draw_rhatplot(model3) + labs(title = "Model 3")
```

#### Model 4

```{r}
draw_rhatplot(model4) + labs(title = "Model 4")
```

###

# Conclusion

# Bibliography {-}

# Original computing environment

```{r}
sessionInfo()
```
